Dynein project log

### 2016-09-23 thesis_stuff/thesis_stuff.tex
Add more measurements to thesis_stuff.pdf.

\begin{center}
  \begin{tabular}{| l | l | l | l | l | l |}
    \hline
    & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7\\\hline
    $L_s$ & 12nm & & & &\\ \hline
    $L_t$ &  7nm & & & &\\ \hline
    $R_b$ &  & & & &\\ \hline
    $R_m$ &  7nm & & & &\\ \hline
    $R_t$ &  & & & &\\ \hline
    $\theta_{m}^{Pre}$ & 250$^{\circ}$ & & 171$^{\circ}$ & &\\ \hline
    $\theta_{m}^{Post}$ & 330$^{\circ}$ & & 137.5$^{\circ}$ & &\\ \hline
    $\theta_{b}$ & 56$^{\circ}$ & & & &\\ \hline
    $\theta_{t}$ & 0$^{\circ}$ & & & &\\ \hline
    $k_{ub}$ & $180 s^{-1,a}$ & & & &\\ \hline
    $k_b$ & $5000 s^{-1,b}$ & & & &\\ \hline
  \end{tabular}
\end{center}

@@

\subsection{Stalk and tail length}
Sarlah et. al use stalk and tail lengths of 12 and 14 nm, respectively. We used PyMol to examine the crystal structures 3VKH and XXXX (pre and post-powerstroke) to find
these values.

\section{Interesting Crystal Structures}
\textbf{3VKH} - 2.8A x-ray resolution full dynein motor, from Kon 2012 (2.8A crystal structure of the dynein motor domain). Probably what we'll use to get some equilibrium angles and lengths, though not sure if crystal structures are identical to in vivo structures. Discusses amino acid chemistry of the powerstroke and long-distance MTBD/ATPase communication.\\
\textbf{3J67/3J68} 34A EM structure of pre/post motor (from Structural Mechanism of dynein power stroke 2014). Shows in-depth changes to motor, but appears to only be the six ATPases and possibly buttress.
\textbf{3J1T/3J1U} 9.7A EM structure of tightly/loosly bound tubulin-MTBD binding from (Structural basis for microtubule binding and release by dynein).\\
\textbf{4RH7} 2.3A x-ray crystal structure of dynein motor/stalk with ADP.Vi (pre-stroke) from (Structure of human cytoplasmic dynein-2 primed for its power stroke). Could be another good place to get angles for pre-stroke, since 3VKH is post-stroke.\\

>>>>

\begin{center}
  \begin{tabular}{| l | l | l | l | l | l |}
    \hline
    & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7\\\hline
    $L_s$ & 12nm & & 21.0nm & &\\ \hline
    $L_t$ &  7nm & & 11.15nm & &\\ \hline
    $R_b$ &  & & 1.57nm & &\\ \hline
    $R_m$ &  7nm & & 7.36nm & &\\ \hline
    $R_t$ &  & & & &\\ \hline
    $\theta_{m}^{Pre}$ & 250$^{\circ}$ & & 171$^{\circ}$ & &\\ \hline
    $\theta_{m}^{Post}$ & 330$^{\circ}$ & & 137.5$^{\circ}$ & &\\ \hline
    $\theta_{b}$ & 56$^{\circ}$ & & & &\\ \hline
    $\theta_{t}$ & 0$^{\circ}$ & & & &\\ \hline
    $k_{ub}$ & $180 s^{-1,a}$ & & & &\\ \hline
    $k_b$ & $5000 s^{-1,b}$ & & & &\\ \hline
  \end{tabular}
\end{center}

@@

\subsection{Stalk and tail length}
Sarlah et. al use stalk and tail lengths of 12 and 14 nm, respectively. We used PyMol to examine the crystal structures 3VKH and 4RH7 (pre and post-powerstroke) to find these values. The linker is roughly residues 1250-1510, calculated by eye.\\

\section{Interesting Crystal Structures}
\textbf{3VKH} 2.8A x-ray resolution full dynein motor, from Kon 2012 (2.8A crystal structure of the dynein motor domain). Probably what we'll use to get some equilibrium angles and lengths, though not sure if crystal structures are identical to in vivo structures. Discusses amino acid chemistry of the powerstroke and long-distance MTBD/ATPase communication.\\
\textbf{3J67/3J68} 34A EM structure of pre/post motor (from Structural Mechanism of dynein power stroke 2014). Shows in-depth changes to motor, but appears to only be the six ATPases and possibly buttress.
\textbf{3J1T/3J1U} 9.7A EM structure of tightly/loosly bound tubulin-MTBD binding from (Structural basis for microtubule binding and release by dynein).\\
\textbf{4RH7} 2.3A x-ray crystal structure of dynein motor/stalk with ADP.Vi (pre-stroke) from (Structure of human cytoplasmic dynein-2 primed for its power stroke). Could be another good place to get angles for pre-stroke, since 3VKH is post-stroke.\\
